---
title: "icloudR-vignette"
author: "Bruce Schardt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{icloudR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
library(iexcloudR)
library(tidyquant)
```

## IEX Cloud Api

The IEX Cloud API is a micropayment Api for financial and stock quote data. The Api is hosted by IEX Group Inc. [The Investors Exchange](https://iextrading.com/). Using the Api requires [registration](https://iexcloud.io/cloud-login#/register). There is a free tier for use during initial api exploration and application development. 

- [Pricing](https://iexcloud.io/pricing/)
- [Api Documentation](https://iexcloud.io/docs/api/)

## iexcloudR

This is functional wrapper which returns data as tibbles, with a few exceptions. See the package documentation for call signitures, parameter descriptions, and the micropayment cost of each function call. 

## Security Tokens

During resistration at icloud.io you were given security tokens required to access this API. This wrapper will read those tokens from the .env (or .Renviron) file. The .env file must include the following three key pairs;

```
IEXCLOUD_VERSION = "BETA"
IEXCLOUD_PRIVATE_KEY = "pk_.........."
IEXCLOUD_SECRET_KEY  = "sk_.........."
```

```{r echo=TRUE, fig.height=4, fig.width=6}
AAPL<-historyFor("AAPL",timePeriod = "3m")
# Candlestick Chart
 AAPL %>%
     ggplot(aes(x = date, y = close)) +
     geom_segment(aes(x=date, y = (min(low)+(max(high)-min(low))*(volume/max(volume))), xend = date, yend = min(low)),color="purple",size=0.2) + 
     geom_candlestick(aes(open = open, high = high, low = low, close = close),color_up="black",color_down="black",fill_up="green",fill_down="red",size=0.4) +
   ggtitle("Apple 3 month chart") + ylab("price") 



```

```{r echo=TRUE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
intraday <-historyFor("AAPL",date ="2019-05-22",chartIEXOnly = TRUE)
# Candlestick Chart
 intraday %>%
     ggplot(aes(x = minute, y = close)) +
     geom_candlestick(aes(open = open, high = high, low = low, close = close),color_up="black",color_down="black",fill_up="green",fill_down="red",size=0.3) +
   ggtitle("Apple Intraday chart") + ylab("price") +
   scale_x_continuous(name = "time (America/New_York)",breaks = c(0,30,90,150,210,270,330,390), labels =c('9:30','10','11','12','1','2','3','4'));

```



> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
